Paper 2: Vitamin D

### 2017-11-06 doc/vitaminD.Rmd
removed PTH from vitamin D model

# gee_vitd_baseline <- ds %>% 
#   prep_mason_data_vitd() %>% 
#   mason_gee(y = c("VitaminD", "PTH"),
#             x = "udbpCrBase",
#             covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
#             intvar = "Season") %>% 
#   mason::polish_renaming(rename_gee_vitd)

@@

plot_gee_results_vitd(gee_vitd_baseline,
                 yvars = c("Serum 25(OH)D (nmol/L)",
                           "PTH (pmol/L)"))

@@

# gee_vitd <- ds %>% 
#   prep_mason_data_vitd() %>% 
#   mason_gee(y = c("lVitD", "lPTH"),
#             x = "udbpCr",
#             covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
#             intvar = "Season") %>% 
#   mason::polish_renaming(rename_gee_vitd)

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = c("lVitD", "lPTH"),
            x = "udbpCr",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

>>>>

@@

plot_gee_results_vitd(gee_vitd_baseline,
                 yvars = "Serum 25(OH)D (nmol/L)")

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCr",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "MET", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)
